### 2013-07-03 cws/emnlp_cws/discussion.tex
a few updates

>>>>

some errors where DD picks the wrong model:
gold: 有 亭台樓閣 流水
CRF: 亭台 樓閣  <-- DD
PCT: 亭台樓閣

gold: 大規模 海陸空 聯合 軍演   
CRF: 大規模 海 陸空 聯合 軍演   <-- DD
PCT: 大規模 海陸空 聯合 軍演

gold: 在 李鄭屋邨 附近
CRF: 在 李鄭屋邨 附近
PCT: 在 李鄭屋 邨 附近   <-- DD

gold: 麥 父 笑說
CRF:  麥 父 笑說
PCT: 麥父 笑說    <-- DD

gold: 天氣 熱 時 冷氣 大 開     
CRF: 天氣 熱 時 冷氣 大 開     
PCT: 天氣 熱時 冷氣 大 開     <-- DD

### 2013-07-03 cws/emnlp_cws/relatedwork.tex
a few updates

See \cite{Sun:2010:COLING} for a good description. We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features. Point out how some of these features basically directly capture the training lexicon.
%
%\subsection{Relative Strength and Weakness}
%Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).  (NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section). But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
% The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV. Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.
%

\subsection{Mixing Models} various mixing approaches have been proposed to combine the merits of these two classes of models \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.

>>>>

Initially word-based segmentation approaches employed simple heuristics like dictionary-lookup maximum matching \cite{Chen:1992:ACL}, contemporary approaches use machine learning techniques to solve an argmax problem of the form:

% add eq

%See \cite{Sun:2010:COLING} for a good description. We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features. Point out how some of these features basically directly capture the training lexicon.
%
%\subsection{Relative Strength and Weakness}
%Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).  (NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section). But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
% The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV. Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.
%

\subsection{Mixing Models} Since the two types of models described above have different strengths and make different kinds of errors, various mixing approaches have been proposed to combine them \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.
